Missing data: Current practice in football research and recommendations for reporting missingness

### 2020-09-03 paper/paper.Rmd
update details of the search

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@Schafer2002] **(should this reference be here?)**. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The search process is
summarised in Figure 1.

```{r prisma-example, eval = FALSE}
require(PRISMAstatement)

prisma()

[[https://cran.r-project.org/web/packages/PRISMAstatement/vignettes/PRISMA.html]{.ul}](https://cran.r-project.org/web/packages/PRISMAstatement/vignettes/PRISMA.html)

library(PRISMAstatement)

e.g.,

prisma(found = 3863,

found_other = NA,

no_dupes = 1909,

screened = 1954,

random_sample = 199,

full_text = 199,

full_text_exclusions = 62,

width = 800, height = 800)
```

**Figure 1.** PRISMA flow chart.

Our intention was to survey, at random, 10% of the total articles found
(after title and abstract screening). We were primarily interested in
whether missing data were reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information about how missing
values were handled was also extracted (see Supplement 1). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval. Supplement 1 provides
further details of the search.

>>>>

To estimate the proportion of articles that report missing data in
football research, we conducted a systematic search [@Schafer2002] **(should this reference be here?)**. Football related
articles published in 2019 were studied. Three major sports medicine
databases (SPORTDiscus, Embase and Cinahl) were searched, using key
terms and search limits (Supplement 2). Included articles were: (a) written in English; (b) had an accessible
full-text; and (c) included quantitative data. The search process is
summarised in the PRISMA figure provided in Supplement 2.

Our intention was to survey, at random, 10% of the total articles found
(after title and abstract screening). We were primarily interested in
whether missing data were reported or acknowledged; and if not, whether
a dataset was shared. Where applicable, information about how missing
values were handled was also extracted (see Supplement 2). Two authors
independently extracted the data (X% agreement). Findings are reported
as the proportion and 95% confidence interval. Supplement 2 provides
further details of the search.
